%% =========================================================================
%%  Abstract (English)
%% =========================================================================

\begin{otherlanguage}{english}

\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

\noindent
The thesis develops a family of quasi-Newton Jacobian updates that
\emph{preserve past secant conditions}, and applies them to nonlinear
systems, smooth unconstrained optimisation and strongly monotone
variational inequalities (VI).

We first derive a general rank-$m$ parameterisation
$B_{k+1} = \widehat{B}_k + (Y_m - \widehat{B}_k S_m)
  (V_m^{\top} S_m)^{-1} V_m^{\top}$
covering classical Broyden, Anderson acceleration, and Frobenius-minimal
multisecant updates. Inside this family we construct
\textbf{SP-Broyden}~--- a rank-1 update that exactly preserves $p$ most
recent secant conditions via the choice
$v_k^{*} = S_p G_p^{-1} e_1$, where $G_p = S_p^{\top} S_p$
is the window Gram matrix. We prove a Frobenius-minimality theorem
and an \emph{improved bounded-deterioration} bound
$\|E_{k+1}\|_F^2 \le \|E_k\|_F^2
   + O\!\bigl(\sigma_{\min}^{-2}(S_p)\sum_j \|x_j-x^{*}\|^2 \|s_j\|^2\bigr)$,
i.e.\ the increment is \emph{quadratic} in the distance to the solution
rather than linear.

For the symmetric case we prove an incompatibility theorem stating that
preserving all past secants is incompatible with symmetry, and resolve
the incompatibility by \textbf{SS-U}, a secant-stabilised symmetric update
that corrects the residual in the orthogonal complement $s_k^{\perp}$.
SS-U inherits superlinear convergence (Dennis--Mor\'e criterion)
and empirically enlarges the basin of attraction by a factor of
$1.5$--$2$ over SR1 on the Curved Valley family.

Applied to strongly monotone VI, the improved bounded-deterioration
property of SP-Broyden lifts the $O(T^{-1})$ barrier of VIQA-Broyden.
We prove a locally optimal rate theorem for VIJI${+}$SP-Broyden and
an unconditional optimal-rate theorem
$\mathrm{GAP} = O(L_1 D^3 / T^{3/2})$ for the guaranteed variant
\textbf{SP-AFD}, which uses one finite-difference refinement per
iteration.

All theoretical results are verified numerically on Discrete~BVP,
Broyden~Banded, Curved~Valley and a family of cubic strongly monotone~VI.

\vspace{1em}\noindent
\textbf{Keywords:} quasi-Newton methods, classical and multisecant
Broyden, SR1, BFGS, symmetric updates, bounded deterioration,
superlinear convergence, variational inequalities, VIJI-Restarted,
optimal convergence rate.

\end{otherlanguage}
