\begin{thebibliography}{99}

\bibitem{broyden1965}
  Broyden C.\,G. A class of methods for solving nonlinear simultaneous equations //
  Math.~Comp. 1965. V.~19(92). P.~577--593.

\bibitem{anderson1965}
  Anderson D.\,G. Iterative procedures for nonlinear integral equations //
  J.~ACM. 1965. V.~12(4). P.~547--560.

\bibitem{dennis1977}
  Dennis J.\,E., Mor{\'e} J.\,J. Quasi-Newton methods, motivation and theory //
  SIAM Rev. 1977. V.~19(1). P.~46--89.

\bibitem{dennis1996}
  Dennis J.\,E., Schnabel R.\,B. Numerical Methods for Unconstrained Optimization
  and Nonlinear Equations. --- Philadelphia: SIAM, 1996.

\bibitem{walker2011}
  Walker H.\,F., Ni P. Anderson acceleration for fixed-point iterations //
  SIAM J.~Numer.~Anal. 2011. V.~49(4). P.~1715--1735.

\bibitem{fang2009}
  Fang H.\,R., Saad Y. Two classes of multisecant methods for nonlinear acceleration //
  Numer.~Linear Algebra Appl. 2009. V.~16(3). P.~197--221.

\bibitem{bfgs}
  Nocedal J., Wright S.\,J. Numerical Optimization. --- New York: Springer, 2006.

\bibitem{lbfgs}
  Nocedal J. Updating quasi-Newton matrices with limited storage //
  Math.~Comp. 1980. V.~35(151). P.~773--782.

\bibitem{schnabel1983}
  Schnabel R.\,B. Quasi-Newton methods using multiple secant equations.
  Technical Report, DTIC, 1983.

\bibitem{more1981}
  Mor{\'e} J.\,J. [et~al.]. Testing unconstrained optimization software //
  ACM Trans.~Math.~Softw. 1981. V.~7(1). P.~17--41.

\bibitem{Agafonov2024VIJI}
  Agafonov~A., Ostroukhov~P., Mozhaev~R. [et~al.].
  Exploring Jacobian inexactness in second-order methods
  for variational inequalities:
  lower bounds, quasi-Newton updates, and restarts //
  Proc. 38th Conference on Neural Information Processing Systems (NeurIPS), 2024.
  arXiv:2405.15990.

\bibitem{Lin2022Perseus}
  Lin~T., Jordan~M.\,I.
  Explicit second-order min-max optimization methods
  with optimal convergence guarantee.
  2022. arXiv:2210.12860.

\bibitem{broyden1973}
  Broyden C.\,G., Dennis J.\,E., Mor{\'e} J.\,J.
  On the local and superlinear convergence of quasi-Newton methods //
  J.~Inst.~Math.~Appl. 1973. V.~12(3). P.~223--245.

\bibitem{dennis1974}
  Dennis J.\,E., Mor{\'e} J.\,J.
  A characterization of superlinear convergence and its application
  to quasi-Newton methods //
  Math.~Comp. 1974. V.~28(126). P.~549--560.

\bibitem{gay1979}
  Gay D.\,M. Some convergence properties of Broyden's method //
  SIAM J.~Numer.~Anal. 1979. V.~16(4). P.~623--630.

\bibitem{davidon1959}
  Davidon W.\,C. Variable metric method for minimization.
  Technical Report ANL-5990 (Rev.), Argonne National Laboratory, 1959.
  Reprinted in SIAM J.~Optim. 1991. V.~1(1). P.~1--17.

\bibitem{fletcher1963}
  Fletcher~R., Powell M.\,J.\,D.
  A rapidly convergent descent method for minimization //
  Comput.~J. 1963. V.~6(2). P.~163--168.

\bibitem{broyden1970}
  Broyden C.\,G. The convergence of a class of double-rank minimization
  algorithms //
  J.~Inst.~Math.~Appl. 1970. V.~6(1). P.~76--90; V.~6(3). P.~222--231.

\bibitem{shanno1970}
  Shanno D.\,F. Conditioning of quasi-Newton methods for function
  minimization //
  Math.~Comp. 1970. V.~24(111). P.~647--656.

\bibitem{powell1970}
  Powell M.\,J.\,D.
  A new algorithm for unconstrained optimization //
  Nonlinear Programming (Rosen J.\,B., Mangasarian O.\,L., Ritter~K., eds.).
  New York: Academic Press, 1970. P.~31--65.

\bibitem{powell1971}
  Powell M.\,J.\,D.
  On the convergence of the variable metric algorithm //
  J.~Inst.~Math.~Appl. 1971. V.~7(1). P.~21--36.

\bibitem{powell1976}
  Powell M.\,J.\,D.
  Some global convergence properties of a variable metric algorithm
  for minimization without exact line searches //
  Nonlinear Programming (SIAM-AMS Proc., Vol.~IX). Providence, RI: AMS,
  1976. P.~53--72.

\bibitem{conn1991}
  Conn A.\,R., Gould N.\,I.\,M., Toint Ph.\,L.
  Convergence of quasi-Newton matrices generated by the symmetric
  rank one update //
  Math.~Programming. 1991. V.~50(1--3). P.~177--195.

\bibitem{li2001}
  Li D.-H., Fukushima~M. A modified BFGS method and its global convergence
  in nonconvex minimization //
  J.~Comput.~Appl.~Math. 2001. V.~129(1--2). P.~15--35.

\bibitem{burdakov1983}
  Burdakov O.\,P.
  Stable versions of the secant method for solving systems of equations //
  U.S.S.R.~Comput.~Math.~Math.~Phys. 1983. V.~23(5). P.~1--10.

\bibitem{byrd1994}
  Byrd R.\,H., Nocedal~J., Schnabel R.\,B.
  Representations of quasi-Newton matrices and their use in limited
  memory methods //
  Math.~Programming. 1994. V.~63(1--3). P.~129--156.

\bibitem{byrd1995}
  Byrd R.\,H., Lu~P., Nocedal~J., Zhu~C.
  A limited memory algorithm for bound constrained optimization //
  SIAM J.~Sci.~Comput. 1995. V.~16(5). P.~1190--1208.

\bibitem{liu1989}
  Liu D.\,C., Nocedal~J. On the limited memory BFGS method for large
  scale optimization //
  Math.~Programming. 1989. V.~45(1--3). P.~503--528.

\bibitem{toth2015}
  Toth~A., Kelley C.\,T. Convergence analysis for Anderson acceleration //
  SIAM J.~Numer.~Anal. 2015. V.~53(2). P.~805--819.

\bibitem{rodomanov2021sr1}
  Rodomanov~A., Nesterov~Yu.
  New results on superlinear convergence of classical quasi-Newton methods //
  J.~Optim.~Theory~Appl. 2021. V.~188. P.~744--769.

\bibitem{rodomanov2021bfgs}
  Rodomanov~A., Nesterov~Yu.
  Rates of superlinear convergence for classical quasi-Newton methods //
  Math.~Programming. 2022. V.~194. P.~159--190.

\bibitem{ye2022nonasymp}
  Ye~H., Luo~L., Zhang~Z.
  A nonasymptotic superlinear convergence rate of quasi-Newton methods.
  2022. arXiv:2003.13607.

\bibitem{jin2022sharp}
  Jin~Q., Mokhtari~A.
  Non-asymptotic superlinear convergence of standard quasi-Newton methods //
  Math.~Programming. 2023. V.~200. P.~425--473.

\bibitem{mokhtari2018iqn}
  Mokhtari~A., Eisen~M., Ribeiro~A.
  IQN: An incremental quasi-Newton method with local superlinear
  convergence rate //
  SIAM J.~Optim. 2018. V.~28(2). P.~1670--1698.

\bibitem{monteiro2012}
  Monteiro R.\,D.\,C., Svaiter B.\,F.
  Iteration-complexity of a Newton proximal extragradient method for
  monotone variational inequalities and inclusion problems //
  SIAM J.~Optim. 2012. V.~22(3). P.~914--935.

\bibitem{bullins2022}
  Bullins~B., Lai K.\,A. Higher-order methods for convex-concave
  min-max optimization and monotone variational inequalities //
  SIAM J.~Optim. 2022. V.~32(3). P.~2208--2229.

\bibitem{adil2022}
  Adil~D., Bullins~B., Jambulapati~A., Sachdeva~S.
  Line search-free methods for higher-order smooth monotone
  variational inequalities.
  2022. arXiv:2205.06167.

\bibitem{tseng1995}
  Tseng~P. Further applications of a splitting algorithm to
  decomposition in variational inequalities and convex programming //
  Math.~Programming. 1990. V.~48(1--3). P.~249--263.

\bibitem{fukushima1992}
  Fukushima~M. Equivalent differentiable optimization problems and
  descent methods for asymmetric variational inequality problems //
  Math.~Programming. 1992. V.~53(1--3). P.~99--110.

\end{thebibliography}
